### 2018-10-22 post-linearity-2018/introduction.tex
Couple of changes.

In this paper we show how to add an exchange modality, $eA$, where the
modality now occurs on both operands being exchanged. That is, one can
show that $eA \otimes eB \multimap eB \otimes eA$ holds.  We give a
LNL natural deduction formalization for the Lambek calculus with this
new modality, and two categorical models: a LNL model and a concrete
model in dialectica spaces.  Thus giving a second solution to the
problem proposed above.

>>>>

In this paper we show how to add an exchange modality, $eA$, where the
modality now occurs on both operands being exchanged. That is, one can
show that $eA \otimes eB \multimap eB \otimes eA$ holds.  We give a sequent
calculus and a LNL natural deduction formalization for the Lambek calculus
with this new modality, and two categorical models: a LNL model and a
concrete model in dialectica spaces. Thus giving a second solution to the
problem proposed above.
